\texttt{Taxonomic supertree construction with}\texttt{\emph{ Incertae sedis}}\texttt{ taxa}

### 2018-06-19 doc/incertae_sedis.tex
minor change

Our current supertree algorithm places $T3$ at the MRCA of $T1$ and
$T2$ if $T3$ is a taxonomy-only taxon, but places $T3$ at the root
of the tree if it occurs in an input tree.  This inconsistent behavior
is not restricted to cases that contain \emph{incertae sedis} taxa, but is a
general problem with compatibility-based algorithms that do not retain
partial information from incompatible splits.  Such information could
include compatible triplets that comprise parts of the incompatible split.
The inconsistency results from the fact that our sub-problem solver
implements compatibility-based consensus and completely discards
incompatible splits, while the unpruner implements an \emph{ad hoc}
rule to place pruned taxonomy-only taxa at the MRCA of taxa that occur
in input trees.  It would be desirable to update the sub-problem
solver to be consistent with the unpruner, so that we could treat the
pruning and unpruning steps as an optimization that has no effect on
semantics.

>>>>

Our current supertree algorithm places $T3$ at the MRCA of $T1$ and
$T2$ if $T3$ is a taxonomy-only taxon, but places $T3$ at the root
of the tree if it occurs in an input tree.  This inconsistent behavior
is not restricted to cases that contain \emph{incertae sedis} taxa, but is a
general problem with compatibility-based algorithms that do not retain
partial information from incompatible splits.  Such information could
include compatible triplets that comprise parts of the incompatible split.
The inconsistency results from the fact that our sub-problem solver
implements compatibility-based consensus and completely discards
incompatible splits, while the unpruner implements an \emph{ad hoc}
rule to place pruned taxonomy-only taxa at the MRCA of taxa that occur
in input trees.  It would be desirable to update the sub-problem
solver to be consistent with the unpruner, so that we could treat the
pruning and unpruning steps as an optimization that has no effect on
which tree is returned.
